Higher-Order unification for free!

### 2024-04-12 paper/main.tex
the abstract has to fit 1 column

\keywords{Logic Programming, Meta-Programming, Higher-Order Unification, Proof Automation}

@@

\paragraph{Decompilation}
A failure is thrown if any \linkbeta remains in \linkStore at the
begin of decompilation, i.e. all \linkbeta should be solved before decompilation.

>>>>

\keywords{Logic Programming, Meta-Programming, Higher-Order Unification}

@@

\paragraph{Decompilation}
All \linkbeta should be solved before decompilation.
If any \linkbeta remains in \linkStore, decompilation fails.
